Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-05 doc/PRF2022/PRF_main.tex

\begin{abstract}
  Active colloidal systems with non-equilibrium self-organization is a
  long-standing, challenging area in biology. To understand how
  hydrodynamic flow may be used to actively control self-assembly of
  Janus particles (JPs), we use a model recently developed for the
  many-body hydrodynamics of amphiphilic JPs suspended in a viscous
  background flow (JFM, 941, 2022). We investigate how various 
  morphologies arise from tuning the hydrophobic distribution of the
  JP-solvent interface.  
  We found JPs assembled into uni-lamella,
  multi-lamella and striated structures. To introduce dynamics, we
  include a linear shear flow and a Taylor-Green mixing flow, and
  measure the collective dynamics of JP particles in terms of their (a)
  free energy from the hydrophobic interactions between the JPs, (b)
  order parameter for the ordering of JPs in terms of alignment of their
  directors, and (c) strain parameter that captures the deformation in
  the assembly. We characterized the effective material properties of
  the JP structures and found that the uni-lamellar structures increases
  orientation order under shear flow, the multilamellar structure
  behaves as a shear thinning fluid, and the striated structure
  possesses a yield stress. These numerical result provide
  insights into dynamic control of non-equilibrium active biological
  systems with similar self-organization.
\end{abstract}

@@

\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
Janus particles are colloids combining two dissimilar chemical or
physical functionalies at their opposite sides\cite{KirillovaMarschelkeSynytska2019}.
Self-propelling Janus particles, for example, with a permanent biphasic asymmetry,
have emerged as a rich chemical platform for the exploration of active matter\cite{Meredithetal2022}.
In the absence of mobility and any imposed flow, Janus particles often self-assemble into
structures in a viscous solvent with tunable functions for biomedical engineering
applications~\cite{GheisariSahfieeAbbasiEtAl2021_DMR,
LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale, Bradley2016,Zarzaretal2015,KirillovaMarschelkeSynytska2019}.
Depending on the interactions between Janus particles (JPs) and the
surrounding viscous solvent, JPs self-assemble into oligomers of various
geometries and sizes~\cite{Bradley2017,KangHonciuc2018,HongCacciutoLuijtenGranick2008}.

When driven by an external flow, 
dynamic rearrangement of JPs emerges naturally from the interactions between particles and fluid in colloidal
matter~\cite{RevModPhys.93.025008}.
Such colloidal hydrodynamics belongs to a wide class of
nonequilibrium self-organization in physics, often with complexity and features similar to that of 
biological systems such as living cells, bacterial baths, and
animal flocks~\cite{CollardGrosjeanVandewalle2020,Vutukuri2020}. A
long-standing challenge in fluid mechanics and material science is to
solve the ``inverse" problem of creating a model colloidal system that
will self-assemble into a prescribed
structure~\cite{PhysRevLett.128.256102}. For example, the framework of
geometrical frustration, which has been used to explain disordered
systems, could instead be used to design new, ordered systems, through
specific choices for the shapes or interactions of the
particles~\cite{Manoharan2015_Science}.

The surface of a Janus particle may have
a dissimilar spatial distribution of hydrophobicity\cite{doi:10.1021/la503455h}.
The many-body hydrodynamics of amphiphilic Janus particles assembled as
vesicles suspended in a viscous fluid in the inertialess regime (zero Reynolds number) has
been studied using boundary integral numerical
simulations~\cite{Fu20,Fu2022_JFM}. The dynamics of the JP suspension
results from the combination of long-range hydrodynamic interaction and
non-local interactions between JPs through the distribution of a
hydrophobic attraction potential (HAP).
%
In a quiescent flow, numerical simulations of a JP suspension showed
self-assembly into micelles and bilayers of JPs that provide an
alternative means for computing the mechanical moduli of a colloidal
membrane~\cite{NaTr00,Fu20,KrFiGuKaHa13}. Under background flows, the
hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs) exhibit
many familiar behaviors of a vesicle: elongation and
alignment along the extensional direction, tank-treading, and rupture of
a vesicle under shear
flow~\cite{Fu2022_JFM,grandmaison_brancherie_salsac_2021,D2SM00179A,keller_skalak_1982,Finken08,Shaqfeh11}.

Molecular dynamics (MD) and Monte Carlo provide another avenue for
simulating the interaction between JPs, solvents, and
substrates\cite{Brandner2019,Baniketal2021,HongCacciutoLuijtenGranick2008,C9NR05885K}.
These methods often use pair-potentials to describe the
interaction between JPs, for example by prescribing angle
dependent forces and torques that bring the
hydrophobic sides of two amphiphilic JPs into opposition.
The HAP formulation of the present work also has attractive, long-range forces and torques,
but they are instead derived from a boundary value problem for the molecular
structure of water\cite{Ma77, GoHaKo94,ErLjCl89,Lietal05,Israelachvili80}.
Unlike in MD or Monte Carlo-based simulations,
the HAP interactions are nonadditive\cite{Fu20}, so that
the interactions between a pair of JP is affected by the presence of other particles.

In this work, we take advantage of the flexibility of the HAP model to
examine the effects of varying the distribution of hydrophobicity on JP surfaces.
Such variation of the boundary condition on JP surfaces have been realized experimentally
by using chemicals to adjust the polarity of the viscous solvent, for example
\cite{Zarzaretal2015,KirillovaMarschelkeSynytska2019,doi:10.1021/la503455h}.
We show that a simple tuning of the hydrophobic distribution leads to transitions from unilamellar to
multilamellar or striated superstructures of JPs. 
Focusing on the fluid-structure interactions that correspond to such transitions, 
we investigate the deformation of these
novel structures in background flows and map out their collective
behavior away from equilibrium.
Looking forward, including other fields like
electric potential for JPs synthesized with
charged polymers\cite{HongCacciutoLuijtenGranick2008,doi:10.1021/la503455h,KangHonciuc2018},
is straightforward within the context of the boundary integral representations\cite{kohl-cor-che-vee22},
opening further lines of investigation.

@@

\section{Model parameters and boundary conditions}
The interactions generated by the HAP-mobility problem formulation
\eqref{eq:stokes}--\eqref{eq:force}
lead to particle self-assembly for a broad range of parameters and
boundary conditions.  Generally speaking, the effective distance of the
hydrophobic interaction is set by the screening length $\rho$.
Smaller values of the repulsion distance $\rho_0$ decrease the distance
where attraction and repulsion are in balance and lead to more compact
particle assemblies. 
The rate of self assembly is proportional to the interfacial tension $\gamma$,
and inversely proportional to solvent viscosity $\mu$; it is
roughly inversely proportional to screening length $\rho.$

To give our system physical units, we set the model parameters
using phospholipids as a characteristic amphiphile in water \cite{Boal}.
For solvent viscosity, we use $\mu = 1$ mPa s for the viscosity
of water at room temperature.
Pure lipid components give a range
of interfacial tensions $0.7$ -- $5.3$ pN nm$^{-1}$
~\cite{KUZMIN2005, Petelska2012,Jackson2016,GarciaSaez}.
As in our previous works\cite{Fu20,Fu2022_JFM},
we use $\gamma=4.1$ pN nm$^{-1}$ since this value gave
good agreement with elastic moduli of lipid bilayers.
The particle radius $c = 1.25$ nm
gives a diameter representative of phospholipid length \cite{Boal},
and the screening length $\rho = 5$ nm
derives from experimental force-distance measurements of hydrophobic
attraction \cite{ErLjCl89,Lietal05,Israelachvili80,Jackson2016}.
Based on empirical studies, the repulsion modulus $M = 2$ pN
and repulsion distance $\rho_0 = 0.5$ nm give an interparticle
distance around one particle radius.  This 
ensures the accuracy of the boundary integral representations
\eqref{eq:SL_BIE} and \eqref{eq:velocity}
without having to employ overly aggresive mesh refinement. 
Altogether, the above parameter set gives
a characteristic time $1$
ns and characteristic length $1$ nm.

\begin{figure}[h!]
\begin{center}
  \includegraphics[width=\textwidth]{Figures/Figure0.pdf}
\end{center}
\begin{caption}{\label{fig:boundary_conditions}
    The leftmost diagram illustrates the particle
    $\Gamma_i$ with center $\aa_i$, radius $c$, and director $\dd$,
    along with the angle $\alpha$ used to define $g(\xx)$ in \eqref{eq:bc-type}.
    The three righ plots show $g(\xx)$ (black curve) for BC (i), (ii), and (iii)
    when $\dd = (1,0)$. The surfaces are the respective solutions
    $u(\xx)$ of \eqref{eq:SL} for a single, isolated particle.  
  }
\end{caption}
\end{figure}

@@

@@

In this work, we employ the newly developed JP model using BIEs ~\cite{Fu20, Fu2022_JFM} 
and tune the boundary conditions with energy normalization to study the  collective dynamics of 
amphiphilic (BC(i)), biased hydrophobic (BC (ii)), and bipolar (BC(iii)) JPs under various flowing conditions (quiescent flow, linear shear flow, and Taylor-Green flow).
Three quantities are computed to characterize the dynamics of the collective configurations of JPs: Free energy $F$, strain parameter $E$ and 
scalar order parameter $S_2$. In this numerical study we quantify how the collective hydrodynamics of JPs is affected by an external flow. 
Under a given flow, we use these three measures of deformations to quantify the differences in the collective dynamics between the three types of JPs.
These results, summarized below, may provide some general insight into the dynamic control of active particles in a viscous suspension.

Within the framework of boundary integral equations, we derive a convenient expression for computing the free energy using the single layer potential (see 
equation~\eqref{eq:normal_deriv}). In a quiescent flow, the free energy profiles demonstrate that the relaxation process for 
particles confined in a certain size of box is independent of number of particles 
($N_b$). However, we did find the final configurations to depend on the initial distribution of particle 
directors $\dd_i$. Therefore, multiple patterns or local energy minimum states may 
appear depending on the initial setup.

Under a relatively weak linear shear flow, the amphiphilic (BC (i)) JPs behave as a unilamellar vesicle that elongates and tank-treads, with the scalar order 
parameter increasing over time.
For the multi-lamella (BC (ii)) and the striated (BC (iii)) structures  the assembly of JPs behaves like a rigid body with minimal deformation. The effective 
viscosity of the material gives a quantitative validation to support the statement. High 
shear-rate cases provide a range for critical shear rates where the structures break 
apart and undergo major topological changes. 
We further showed that
free energy, scalar order parameter, and strain are effective measures to quantitatively capture the dynamics of the JP oligomers under a linear shear flow.

Under a Taylor-Green flow,  we find that the amphiphilic JPs to be most interesting, exhibiting different vesicle shapes depending on the ratio of the size of the
TG flow to the vesicle size. These results show that we can control the shape of the vesicle to be a square shape or a polygonal shape by adjusting the size of
the cell in TG flow. On the other hand, the assembly of multi-lamella JPs and the striated JPs behaves more or less as a rigid body with connected subdomains, with the number of subdomains increasing with stronger strength of the TG flow. Overall, we found that the multilamellar (BC (ii)) JPs oligomers behave as a shear-thinning fluid, while the striated (BC (iii)) JPs oligomers possess a yield stress.

The results reported here provide an inroad modeling framework for hydrodynamics of active colloids
\cite{Meredithetal2022,McGlassonBradley2021,Vutukuri2020,Mallory2017}. 
The present study also helps us understand the rheology of JP oligomers that may be realized in the experiments.
We are now extending this study to three dimensional systems with more realistic features such as size distributions of JPs
and thermal fluctuations\cite{kohl-cor-che-vee22}.
%
 %it has been included in our future goals\cite{kohl-cor-che-vee22}.
From a numerical perspective,
it is straightforward to include
random perturbations in the particle shape and
boundary condition that mimick interfacial properties
found in lab conditions\cite{Bradley2016,Bradley2017,Zarzaretal2015,doi:10.1021/la503455h}.

\section{Appendix}
\label{sec:appendix}
Our calculation of the free energy $F$ relied on 
converting the body integral in \eqref{eq:free_energy}
into the surface
integral in \eqref{eq:free_energy2}
involving only single layer potentials and
tangential derivatives. 
This section supplies a proof of identity
\eqref{eq:normal_deriv} used in this conversion.
Let 
\begin{equation}
  \label{eq:SLP}
  \mathcal{S}[\sigma](\xx) = \int_\Gamma G(\xx-\yy) \sigma(\yy)\, \dif s_\yy
\end{equation}
be the single layer potential for a density function $\sigma.$
Fix $\xx \in \Gamma$,
let $\nnu_{\xx} = \nnu(\xx)$ and $\nnu_{\yy}$ be the unit normal at $\xx$, respectively $\yy$, in $\Gamma$,
and let $\zz \in \Omega$.  The subscripts in $\nabla_{\zz}$ and $\nabla_{\yy}$ denote
differentiation with respect to $\zz$, respectively $\yy$.

Recall from \eqref{eq:SL_BIE} that $u = \mathcal{D}[\sigma]$.
Then  
\begin{align*}
\nabla_{\zz} u(\zz) \cdot \nnu_{\xx}
&=\nnu_\xx \cdot \nabla_\zz \int_\Gamma \frac{\partial G(\zz-\yy)}{\partial \nnu_\yy}\sigma(\yy) \,\dif s_\yy\\
&=\int_\Gamma \nnu_\xx^\top \left(\nabla_\zz\nabla_\yy^\top  G(\zz-\yy)\right) \nnu_\yy\sigma(\yy)  \,\dif s_\yy\\
  &=-\int_\Gamma \nnu_\xx^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\nnu_\yy\sigma(\yy)\ \dif s_\yy,
\end{align*}
since we can interchange $\nabla_\zz$ with $-\nabla_\yy$.
Following \cite{Hsiao2008}, \S 1.2,
\[
\nnu_\xx^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\nnu_\yy
=
-\tt_{\xx}^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\tt_{\yy}
+ \Delta_{\yy}G(\zz-\yy) \tt_{\xx}\cdot \tt_{\yy}.
\]
Then, using that $\Delta_{\yy} G(\zz-\yy) = \rho^{-2} G(\zz-\yy)$,
interchanging $\nabla_\yy$ with $-\nabla_\zz$ once more,
and integrating by parts in arclength $s$,
we obtain 
\begin{align*}
\nabla_{\zz} u(\zz) \cdot \nnu_{\xx}
&=-\int_\Gamma  \Delta_\yy G(\zz-\yy) {\bf t}_\xx \cdot   {\bf t}_\yy \sigma(\yy)\ \dif s_\yy
+\int_\Gamma({\bf t}_\xx\cdot\nabla_\yy)({\bf t}_\yy\cdot\nabla_\yy G(\zz-\yy))\sigma(\yy)\ \dif s_\yy\\
&= -\int_\Gamma \frac{1}{\rho^{2}} G(\zz-\yy) {\bf t}_\xx \cdot {\bf t}_\yy \sigma(\yy)\ \dif s_\yy  
-({\bf t}_\xx\cdot\nabla_\zz)\int_\Gamma \frac{\dif}{\dif s_\yy}G(\zz-\yy) \sigma(\yy)\ \dif s_\yy\\
&= -\frac{1}{\rho^2} {\bf t}_\xx\cdot \int_\Gamma G(\zz-\yy){\bf t}_\yy \sigma(\yy)\ \dif s_\yy + 
({\bf t}_\xx \cdot \nabla_\zz)\int_\Gamma G(\zz-\yy)\frac{\dif }{\dif s} \sigma(\yy)  \dif s_\yy.
\end{align*}
%
Letting $\zz\to\xx\in\Gamma$, and noting that both sides of the equation are continuous,
we obtain \eqref{eq:normal_deriv}.

% If you have acknowledgments, this puts in the proper section head.
\begin{acknowledgments}
We thank Dr.~S\'ebastien Michelin and Dr.~Cecile Cottin-Bizzonne from LadHyX - Ecole Polytechnique Institut Polytechnique de Paris for organizing the focus-session ``interfacial active matter'' in the conference APS-DFD 2021 and the invitation of submitting a special collection paper. 
B.Q. acknowledges support from the Simons Foundation, Mathematics and Physical Sciences-Collaboration Grants for Mathematicians, Award No. 527139.
Y.-N.Y. acknowledges support from NSF (Grants No. DMS 1614863 and No. DMS 195160) and Flatiron Institute, part of Simons Foundation.

>>>>

\begin{abstract}
  Active colloidal systems with non-equilibrium self-organization is a
  long-standing, challenging area in biology. To understand how
  hydrodynamic flow may be used to actively control self-assembly of
  Janus particles (JPs), we use a model recently developed for the
  many-body hydrodynamics of amphiphilic JPs suspended in a viscous
  background flow (JFM, 941, 2022). We investigate how various
  morphologies arise from tuning the hydrophobic distribution of the
  JP-solvent interface. We find JPs assembled into uni-lamella,
  multi-lamella and striated structures. To introduce dynamics, we
  include a linear shear flow and a Taylor-Green mixing flow, and
  measure the collective dynamics of JP particles in terms of their (a)
  free energy from the hydrophobic interactions between the JPs, (b)
  order parameter for the ordering of JPs in terms of alignment of their
  directors, and (c) strain parameter that captures the deformation in
  the assembly. We characterize the effective material properties of the
  JP structures and find that the uni-lamellar structures increases
  orientation order under shear flow, the multilamellar structure
  behaves as a shear thinning fluid, and the striated structure
  possesses a yield stress. These numerical results provide insights
  into dynamic control of non-equilibrium active biological systems with
  similar self-organization.
\end{abstract}

@@

\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
Janus particles are colloids combining two dissimilar chemical or
physical functionalities at their opposite
sides~\cite{KirillovaMarschelkeSynytska2019}. Self-propelling Janus
particles, for example, with a permanent biphasic asymmetry, have
emerged as a rich chemical platform for the exploration of active
matter~\cite{Meredithetal2022}. In the absence of mobility and any
imposed flow, Janus particles often self-assemble into structures in a
viscous solvent with tunable functions for biomedical engineering
applications~\cite{GheisariSahfieeAbbasiEtAl2021_DMR,
LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale,
Bradley2016,Zarzaretal2015, KirillovaMarschelkeSynytska2019}. Depending
on the interactions between Janus particles (JPs) and the surrounding
viscous solvent, JPs self-assemble into oligomers of various geometries
and sizes~\cite{Bradley2017, KangHonciuc2018,
HongCacciutoLuijtenGranick2008}.

When driven by an external flow, dynamic rearrangement of JPs emerges
naturally from the interactions between particles and fluid in colloidal
matter~\cite{RevModPhys.93.025008}. Such colloidal hydrodynamics
belong to a wide class of nonequilibrium self-organization in physics,
often with complexity and features similar to that of biological systems
such as living cells, bacterial baths, and animal
flocks~\cite{CollardGrosjeanVandewalle2020, Vutukuri2020}. A
long-standing challenge in fluid mechanics and material science is to
solve the ``inverse" problem of creating a model colloidal system that
will self-assemble into a prescribed
structure~\cite{PhysRevLett.128.256102}. For example, the framework of
geometrical frustration, which has been used to explain disordered
systems, could instead be used to design new, ordered systems, through
specific choices for the shapes or interactions of the
particles~\cite{Manoharan2015_Science}.

The surface of a Janus particle may have a dissimilar spatial
distribution of hydrophobicity~\cite{doi:10.1021/la503455h}. The
many-body hydrodynamics of amphiphilic Janus particles assembled as
vesicles suspended in a viscous fluid in the inertialess regime (zero
Reynolds number) has been studied using boundary integral numerical
simulations~\cite{Fu20,Fu2022_JFM}. The dynamics of the JP suspension
results from the combination of long-range hydrodynamic interaction and
non-local interactions between JPs through the distribution of a
hydrophobic attraction potential (HAP).
%
In a quiescent flow, numerical simulations of a JP suspension showed
self-assembly into micelles and bilayers of JPs that provide an
alternative means for computing the mechanical moduli of a colloidal
membrane~\cite{NaTr00, Fu20, KrFiGuKaHa13}. Under background flows, the
hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs) exhibit
many familiar behaviors of a vesicle: elongation and alignment along the
extensional direction, tank-treading, and rupture of a vesicle under
shear flow~\cite{Fu2022_JFM, grandmaison_brancherie_salsac_2021,
D2SM00179A,keller_skalak_1982, Finken08, Shaqfeh11}.

Molecular dynamics (MD) and Monte Carlo provide another avenue for
simulating the interaction between JPs, solvents, and
substrates~\cite{Brandner2019, Baniketal2021,
HongCacciutoLuijtenGranick2008, C9NR05885K}. These methods often use
pair-potentials to describe the interaction between JPs, for example by
prescribing angle dependent forces and torques that bring the
hydrophobic sides of two amphiphilic JPs into opposition. The HAP
formulation of the present work also has attractive, long-range forces
and torques, but they are instead derived from a boundary value problem
for the molecular structure of water~\cite{Ma77, GoHaKo94, ErLjCl89,
Lietal05, Israelachvili80}. Unlike in MD or Monte Carlo simulations, the
HAP interactions are nonadditive~\cite{Fu20}, so that the interactions
between a pair of JPs is affected by the presence of other particles.

In this work, we take advantage of the flexibility of the HAP model to
examine the effects of varying the distribution of hydrophobicity on JP
surfaces. Such variation of the boundary condition on JP surfaces has
been realized experimentally by using chemicals to adjust the polarity
of the viscous solvent~\cite{Zarzaretal2015,
KirillovaMarschelkeSynytska2019, doi:10.1021/la503455h}. We show that a
simple tuning of the hydrophobic distribution leads to transitions from
unilamellar to multilamellar or striated superstructures of JPs.
Focusing on the fluid-structure interactions that correspond to such
transitions, we investigate the deformation of these novel structures in
background flows and map out their collective behavior away from
equilibrium. Looking forward, including other fields like electric
potential for JPs synthesized with charged
polymers~\cite{HongCacciutoLuijtenGranick2008, doi:10.1021/la503455h,
KangHonciuc2018}, is straightforward within the context of the boundary
integral representations~\cite{kohl-cor-che-vee22}, opening further
lines of investigation.

@@

\section{Model parameters and boundary conditions} The interactions
generated by the HAP-mobility problem formulation
\eqref{eq:stokes}--\eqref{eq:force} lead to particle self-assembly for a
broad range of parameters and boundary conditions. Generally speaking,
the effective distance of the hydrophobic interaction is set by the
screening length $\rho$. Smaller values of the repulsion distance
$\rho_0$ decrease the distance where attraction and repulsion are in
balance and lead to more compact particle assemblies. The rate of
self-assembly is proportional to the interfacial tension $\gamma$, and
inversely proportional to solvent viscosity $\mu$; it is roughly
inversely proportional to screening length $\rho.$

To give our system physical units, we set the model parameters using
phospholipids as a characteristic amphiphile in water~\cite{Boal}. For
the solvent viscosity, we use $\mu = 1$~mPa~s for the viscosity of water
at room temperature. Pure lipid components give a range of interfacial
tensions $0.7$--$5.3$~pN~nm$^{-1}$~\cite{KUZMIN2005, Petelska2012,
Jackson2016, GarciaSaez}. As in our previous
works~\cite{Fu20,Fu2022_JFM}, we use $\gamma=4.1$~pN~nm$^{-1}$ since
this value gave good agreement with elastic moduli of lipid bilayers.
The particle radius $c = 1.25$~nm gives a diameter representative of
phospholipid length~\cite{Boal}, and the screening length $\rho = 5$~nm
derives from experimental force-distance measurements of hydrophobic
attraction~\cite{ErLjCl89,Lietal05,Israelachvili80,Jackson2016}. Based
on empirical studies, the repulsion modulus $M = 2$~pN and repulsion
distance $\rho_0 = 0.5$~nm give an interparticle distance around one
particle radius. This ensures the accuracy of the boundary integral
representations~\eqref{eq:SL_BIE} and~\eqref{eq:velocity} without having
to employ overly aggressive mesh refinement. Altogether, the above
parameter set gives a characteristic time $1$~ns and characteristic
length $1$~nm.

@@

\begin{figure}[h!]
\begin{center}
  \includegraphics[width=\textwidth]{Figures/Figure0.pdf}
\end{center}
\begin{caption}{\label{fig:boundary_conditions} The leftmost diagram
  illustrates the particle $\Gamma_i$ with center $\aa_i$, radius $c$,
  and director $\dd$, along with the angle $\alpha$ used to define
  $g(\xx)$ in~\eqref{eq:bc-type}. The three right plots show $g(\xx)$
  (black curve) for BC (i), (ii), and (iii) when $\dd = (1,0)$. The
  surfaces are the respective solutions $u(\xx)$ of~\eqref{eq:SL} for a
  single, isolated particle.}
\end{caption}
\end{figure}

@@

In this work, we employ the newly developed JP model using
BIEs~\cite{Fu20, Fu2022_JFM} and tune the boundary conditions with
energy normalization to study the collective dynamics of amphiphilic
(BC(i)), biased hydrophobic (BC (ii)), and bipolar (BC(iii)) JPs under
various flowing conditions (quiescent flow, linear shear flow, and
Taylor-Green flow). Three quantities are computed to characterize the
dynamics of the collective configurations of JPs: free energy $F$,
strain parameter $E$, and scalar order parameter $S_2$. 
%We quantify how
%the collective hydrodynamics of JPs is affected by an external flow.
Under a given flow, we use these three measures of deformations to
quantify the differences in the collective dynamics between the three
types of JPs. These results, summarized below, provide general insight
into the dynamic control of active particles in a viscous suspension.

Within the framework of boundary integral equations, we derive a
convenient expression for computing the free energy using the single
layer potential (see equation~\eqref{eq:normal_deriv}). In a quiescent
flow, the free energy profiles demonstrate that the relaxation process
for particles confined in a certain size of box is independent of the
number of particles. However, we find that the final configurations does
depend on the initial distribution of particle directors $\dd_i$.
Therefore, multiple patterns or local energy minimum states may appear
depending on the initial setup.

Under a relatively weak linear shear flow, the amphiphilic JPs behave as
a unilamellar vesicle that elongates and tank-treads, with the scalar
order parameter increasing over time. The assembly of multi-lamella and
striated JP structures resemble a rigid body motion with minimal
deformation. The effective viscosity of the material quantitatively
validates this result. High shear-rate cases provide a range of critical
shear rates where the structures break apart and undergo topological
changes. We further show that free energy, scalar order parameter, and
strain are effective measures to quantitatively capture the dynamics of
the JP oligomers under a linear shear flow.

Under a Taylor-Green flow, the amphiphilic JPs are the most interesting,
exhibiting different vesicle shapes depending on the ratio of the size
of the TG flow to the vesicle size. These results show that the shape of
the vesicle, whether square or polygonal, can be controlled by adjusting
the size of the cell in the TG flow. On the other hand, the assembly of
multi-lamella JPs and the striated JPs behave more like a rigid body
with connected subdomains, and the number of subdomains increases with
increasing strength of the TG flow. Overall, the multilamellar (BC (ii))
JPs oligomers behave as a shear-thinning fluid, while the striated (BC
(iii)) JPs oligomers possess a yield stress.

The results reported here provide an inroad modeling framework for
hydrodynamics of active colloids~\cite{Meredithetal2022,
McGlassonBradley2021, Vutukuri2020, Mallory2017}. The present study also
helps us understand the rheology of JP oligomers that may be realized in
the experiments. We are extending this study to three dimensional
systems with more realistic features such as size distributions of JPs
and thermal fluctuations~\cite{kohl-cor-che-vee22}. From a numerical
perspective, it is straightforward to include random perturbations in
the particle shape and boundary condition that mimic interfacial
properties found in lab conditions~\cite{Bradley2016, Bradley2017,
Zarzaretal2015, doi:10.1021/la503455h}.

\section{Appendix}
\label{sec:appendix}
Our calculation of the free energy $F$ relied on converting the body
integral in~\eqref{eq:free_energy} into the surface integral
in~\eqref{eq:free_energy2} involving only single layer potentials and
tangential derivatives. This section supplies a proof of
identity~\eqref{eq:normal_deriv} used in this conversion.  Let 
\begin{equation}
  \label{eq:SLP}
  \mathcal{S}[\sigma](\xx) = \int_\Gamma G(\xx-\yy) \sigma(\yy)\, \dif s_\yy
\end{equation}
be the single layer potential for a density function $\sigma.$ Fix $\xx
\in \Gamma$, let $\nnu_{\xx} = \nnu(\xx)$ and $\nnu_{\yy}$ be the unit
normal at $\xx$, respectively $\yy$, in $\Gamma$, and let $\zz \in
\Omega$. The subscripts in $\nabla_{\zz}$ and $\nabla_{\yy}$ denote
differentiation with respect to $\zz$, respectively $\yy$.

Recall from~\eqref{eq:SL_BIE} that $u = \mathcal{D}[\sigma]$.
Then  
\begin{align*}
\nabla_{\zz} u(\zz) \cdot \nnu_{\xx}
&=\nnu_\xx \cdot \nabla_\zz \int_\Gamma \frac{\partial G(\zz-\yy)}{\partial \nnu_\yy}\sigma(\yy) \,\dif s_\yy\\
&=\int_\Gamma \nnu_\xx^\top \left(\nabla_\zz\nabla_\yy^\top  G(\zz-\yy)\right) \nnu_\yy\sigma(\yy)  \,\dif s_\yy\\
  &=-\int_\Gamma \nnu_\xx^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\nnu_\yy\sigma(\yy)\ \dif s_\yy,
\end{align*}
since we can interchange $\nabla_\zz$ with $-\nabla_\yy$.
Following~\cite{Hsiao2008}, \S 1.2,
\begin{align}
\nnu_\xx^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\nnu_\yy
=
-\tt_{\xx}^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\tt_{\yy}
+ \Delta_{\yy}G(\zz-\yy) \tt_{\xx}\cdot \tt_{\yy}.
\end{align}
Then, using that $\Delta_{\yy} G(\zz-\yy) = \rho^{-2} G(\zz-\yy)$,
interchanging $\nabla_\yy$ with $-\nabla_\zz$ once more, and integrating
by parts in arclength $s$, we obtain 
\begin{align*}
\nabla_{\zz} u(\zz) \cdot \nnu_{\xx}
&=-\int_\Gamma  \Delta_\yy G(\zz-\yy) {\bf t}_\xx \cdot   {\bf t}_\yy \sigma(\yy)\ \dif s_\yy
+\int_\Gamma({\bf t}_\xx\cdot\nabla_\yy)({\bf t}_\yy\cdot\nabla_\yy G(\zz-\yy))\sigma(\yy)\ \dif s_\yy\\
&= -\int_\Gamma \frac{1}{\rho^{2}} G(\zz-\yy) {\bf t}_\xx \cdot {\bf t}_\yy \sigma(\yy)\ \dif s_\yy  
-({\bf t}_\xx\cdot\nabla_\zz)\int_\Gamma \frac{\dif}{\dif s_\yy}G(\zz-\yy) \sigma(\yy)\ \dif s_\yy\\
&= -\frac{1}{\rho^2} {\bf t}_\xx\cdot \int_\Gamma G(\zz-\yy){\bf t}_\yy \sigma(\yy)\ \dif s_\yy + 
({\bf t}_\xx \cdot \nabla_\zz)\int_\Gamma G(\zz-\yy)\frac{\dif }{\dif s} \sigma(\yy)  \dif s_\yy.
\end{align*}
%
Letting $\zz\to\xx\in\Gamma$, and noting that both sides of the equation
are continuous, we obtain~\eqref{eq:normal_deriv}.

% If you have acknowledgments, this puts in the proper section head.
\begin{acknowledgments}
We thank Dr.~S\'ebastien Michelin and Dr.~Cecile Cottin-Bizzonne from LadHyX - Ecole Polytechnique Institut Polytechnique de Paris for organizing the focus-session ``interfacial active matter'' in the conference APS-DFD 2021 and the invitation of submitting a special collection paper. 
B.Q.~acknowledges support from the Simons Foundation, Mathematics and Physical Sciences-Collaboration Grants for Mathematicians, Award No. 527139.
Y.-N.Y.~acknowledges support from NSF (Grants No. DMS 1614863 and No. DMS 195160) and Flatiron Institute, part of Simons Foundation.
